---
title: "Effect Of Attributes On Ratings Of Bars And Restaurants"
author: "Swapnil Jamthe"
date: "18 November 2015"
output: pdf_document
---

##Introduction
There are varoius attributes about Bars & Restaurants.This study is about the effects of various attributes on ratings of the Bars & Restaurants. This will be helpful for the owners to know which attributes matter when they have to make a choice.  

#Methods and Data
Following processing was done on data.  
1) Attributes for businesses,their ratings by different uers were tied into single table.  
2) Attributes having more than 20% missing data were ignored  
3) Rows having all the data were only considered.Total rows considered were 859933.  

Linear regression model was fitted to predict rating(stars) considering attributes as predictors. Following were the attributes with their values considered as predictors.

```{r echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
library(knitr)
```


```{r echo=FALSE}

predictors<-data.frame(attribute=character(),values=character())
predictors<-rbind(predictors,data.frame(attribute="Good For Groups",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Outdoor Seating",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Price Range",values="1,2,3 or 4"))
predictors<-rbind(predictors,data.frame(attribute="Good for Kids",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Alcohol",values="full_bar,none or beer_and_wine"))
predictors<-rbind(predictors,data.frame(attribute="Noise Level",values="average,loud,quiet or very_loud"))
predictors<-rbind(predictors,data.frame(attribute="Has TV",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Attire",values="casual,dressy or formal"))
predictors<-rbind(predictors,data.frame(attribute="Delivery",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Takes Reservations",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Waiter Service",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Wi-Fi",values="no,free or paid"))
predictors<-rbind(predictors,data.frame(attribute="Caters",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Ambience Romantic",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Ambience Intimate",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Ambience Classy",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Ambience Hipster",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Ambience Divey",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Ambience Touristy",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Ambience Trendy",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Ambience Upscale",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Ambience Casual",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Good for latenight",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Good for lunch",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Good for dinner",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Good for breakfast",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Good for brunch",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Parking garage",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Parking street",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Parking validated",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Parking lot",values="true or false"))
predictors<-rbind(predictors,data.frame(attribute="Parking valet",values="true or false"))

kable(predictors,caption="Attributes considered")

```

Variance inflation factor was calculated for all the predictors. Maximum VIF found was around 4.5.Most of them were around 1.Thus multicolinearity can be ignored and coefficients can be studied.

```{r echo=FALSE}

v<-numeric(0)
v<-append(v,1.124976)
v<-append(v,1.271632)
v<-append(v,3.232459)
v<-append(v,2.157787)
v<-append(v,2.805974)
v<-append(v,1.337365)
v<-append(v,1.335678)
v<-append(v,2.416943)

v<-append(v,1.154441)
v<-append(v,1.807307)
v<-append(v,1.932412)
v<-append(v,1.208413)
v<-append(v,1.349727)
v<-append(v,1.441641)
v<-append(v,1.197176)
v<-append(v,2.081782)

v<-append(v,1.546393)
v<-append(v,1.470151)
v<-append(v,1.243490)
v<-append(v,2.600213)
v<-append(v,1.673906)
v<-append(v,4.528098)
v<-append(v,1.224083)
v<-append(v,1.636138)

v<-append(v,1.619866)
v<-append(v,1.445828)
v<-append(v,1.193618)
v<-append(v,2.510972)
v<-append(v,1.805026)
v<-append(v,1.061727)
v<-append(v,2.876013)
v<-append(v,1.692608)

hist(v,main="Histogram for VIFs",xlab="VIF value")
```

##Results

```{r echo=FALSE}
topPositiveFrame<-data.frame(Attribute=character(),Coefficient=numeric())
topPositiveFrame<-rbind(topPositiveFrame,data.frame(Attribute="Attrire formal vs casual",Coefficient=0.4330516))
topPositiveFrame<-rbind(topPositiveFrame,data.frame(Attribute="Ambience Hipster True",Coefficient=0.2455279))
topPositiveFrame<-rbind(topPositiveFrame,data.frame(Attribute="Ambience Classy True",Coefficient=0.2256067))
topPositiveFrame<-rbind(topPositiveFrame,data.frame(Attribute="Ambience Intimate True",Coefficient=0.2146979))
topPositiveFrame<-rbind(topPositiveFrame,data.frame(Attribute="Ambience Romantic True",Coefficient=0.2093387))

kable(topPositiveFrame,caption="Top positive effect of attributes on rating")
```

About attributes  
1) Attire is categorical variable with possible values 'casual','dressy' and 'formal'. 'casual' is the reference category in regression.  
2) Others are binary variables.  

```{r echo=FALSE}
topNegativeFrame<-data.frame(Attribute=character(),Coefficient=numeric())
topNegativeFrame<-rbind(topNegativeFrame,data.frame(Attribute="WiFi Paid vs Free",Coefficient=-0.4422584))
topNegativeFrame<-rbind(topNegativeFrame,data.frame(Attribute="Noise Level Very Loud vs average",Coefficient=-0.4335201))
topNegativeFrame<-rbind(topNegativeFrame,data.frame(Attribute="Ambience Touristy True",Coefficient=-0.2259980))
topNegativeFrame<-rbind(topNegativeFrame,data.frame(Attribute="Alcohol Full Bar vs  Beer and Wine",Coefficient=-0.1859295))
topNegativeFrame<-rbind(topNegativeFrame,data.frame(Attribute="Noise Level Loud vs average",Coefficient=-0.1485293))

kable(topNegativeFrame,caption="Top negative effect of attributes on rating")
```

About attributes  
1) Wifi is categorical variable with possible values 'no', 'free','paid'. 'free' is the reference category in regression.  
2) Noise Level is categorical variable with possible values 'average','loud','quiet','very_loud'. 'average' is the reference category in regression.  
3) Alcohol is categorical variable with possible values 'full_bar','none','beer_and_wine'. 'beer_and_wine' is the reference category in regression.  
4) Ambience Touristy is the binary variable.

##Discussions  
Following are the top observations done during the study.  

Increase in rating is expected by a customer in the following cases  
1) By 0.4330516 when attire is formal formal compared to casual.       
2) By 0.2455279 when ambience is hipster compared to non hipster.      
3) By 0.2256067 when ambience is classy compared to non classy.    
4) By 0.2146979 when ambience is intimate compared to non intimate.   
5) By 0.2093387 when ambience is romantic compared to non romantic.   

Decease in rating is expected by a customer in the following cases  
1) By 0.4422584 when wifi is paid compared to free.   
2) By 0.4335201 when noise level is very loud compared to average.    
3) By 0.2259980 when ambience is touristy compared to non touristy.  
4) By 0.1859295 when there is full bar compared to beer and wine.  
5) By 0.1485293 when noise level is loud compared to average.  







